% !TeX program = xelatex
% Forked from https://www.overleaf.com/latex/templates/modern-deedy/cxtjgrmpsrvh under the Apache license

\documentclass[]{resume-openfont}

% \setlist{nolistsep}

\pagestyle{fancy}
\resetHeaderAndFooter

%--------------------------------------------------------------
% Convenience command - make it easy to fill template

% Create job position command. Parameters: company, position, location, when
\newcommand{\resumeHeading}[4]{\runsubsection{\uppercase{#1}}\descript{ | #2}\hfill\location{#3 | #4}\fakeNewLine}

% Create education heading. Parameters: Name, degree, location, when
\newcommand{\educationHeading}[4]{\runsubsection{#1}\hspace*{\fill}  \location{#3 | #4}\\
\descript{#2}\fakeNewLine}

% Create project heading. Parameters: Name, link, Tech stack
\newcommand{\projectHeading}[3]{\Project{#1}{#2}
\descript{#3}\\}

\newcommand{\projectHeadingWithDate}[4]{\Project{#1}{#2}
\descript{#3 | #4}\\}

% Parameters: courses
\newcommand{\modules}[1]{\textbf{Modules:} #1}

% Parameters: courses
\newcommand{\grades}[1]{\textbf{Grades:} #1}

%--------------------------------------------------------------
\begin{document}

%--------------------------------------------------------------
%     Profile
%--------------------------------------------------------------
\newcommand{\yourName}{Edmund Goodman}
% How you want it to show up on the resume
\newcommand{\yourWebsite}{www.edmundgoodman.co.uk}
% vs how you want it to show up. If it's the same you can just replace "\yourWebsiteLink" with "yourWebsite"
\newcommand{\yourWebsiteLink}{https://www.edmundgoodman.co.uk}
\newcommand{\yourEmail}{cv@edmundgoodman.co.uk}
\newcommand{\githubUserName}{EdmundGoodman}
\newcommand{\linkedInUserName}{EdmundGoodman}

\begin{center}
    \Huge \scshape \latoRegular{\yourName} \\ \vspace{1pt} \small
    %\href{mailto:\yourEmail}{\underline{\yourEmail}} $|$
    \href{\yourWebsiteLink}{\underline{\yourWebsite}} $|$
    \href{https://www.linkedin.com/in/\linkedInUserName}{\underline{linkedIn/\linkedInUserName}} $|$
    \href{https://github.com/\githubUserName}{\underline{github/\githubUserName}}  % $|$
\end{center}

%--------------------------------------------------------------
%     Education
%--------------------------------------------------------------
\section{Education}
% Put school first and degree second if your school is reputable
\educationHeading{BSc (Hons). Computer Science with intercalated year in industry}{University of Warwick $|$ Apple Inc.}{Coventry, UK}{Sept 2020. -- Jun. 2024}

\grades{First year: 1st (80.4\%); Second year: 1st (78.4\%)}
% \modules{Data Structures and Algorithms; Operating Systems;  Computer Security; Software Testing; Advanced Networking; Big Data Analytics}
\sectionsep

%--------------------------------------------------------------
%     Experience
%--------------------------------------------------------------
\section{Work Experience}
\resumeHeading{Apple Inc.}{CAD Design Verification Intern}{St Albans, UK}{Jul. 2022 -- Jun. 2023}
\begin{bullets}  % \begin{itemize}[leftmargin=*, noitemsep]
    \item Built tools and infrastructure for the design and design verification of Apple Silicon in \textbf{Python} and \textbf{Kotlin}.
\end{bullets}  % \end{itemize}
\sectionsep

\resumeHeading{University of Warwick}{iGEM Competitor}{Coventry, UK}{Feb. 2021 -- Sept. 2021}
\begin{bullets}  % \begin{itemize}[leftmargin=*, noitemsep]
    \item Designed the assessed \href{https://2021.igem.org/Team:Warwick}{\underline{wiki website}}, and implemented a \href{https://github.com/EdmundGoodman/Warwick_modelling}{\underline{model of the spread of antibiotic resistant pathogens}}.
\end{bullets}  % \end{itemize}
\sectionsep

\resumeHeading{HUBER+SUHNER Polatis}{Software Engineering Intern}{Cambridge, UK}{Jul. 2020 -- Sept. 2020}
\begin{bullets}  % \begin{itemize}[leftmargin=*, noitemsep]
    \item Updated a testing harness for fibre-optic switches to \textbf{Python 3}, refactored the \textbf{VBA} backend of a corporate planning document, and worked on a \textbf{Java} implementation of the NETCONF call home protocol.
\end{bullets}  % \end{itemize}
\sectionsep

%--------------------------------------------------------------
%     Projects
%--------------------------------------------------------------
\section{Projects}

\projectHeading{Computer Science Revision Guide}{https://warwick.guide/}{Markdown, Java, C, Haskell, Git}{Apr. 2021 -- Present}
\begin{bullets}  % \begin{itemize}[leftmargin=*, noitemsep]
    \item Co-founded and administrated an \textbf{open source} revision resource for the first year Warwick computer science course, used by over 100 students, and with contributions from over 25.
    \item Managed pull requests and issues following open source best practices, communicated with the university to ensure the project was acceptable, and contributed to the notes for every module I took.
\end{bullets}  % \end{itemize}
\sectionsep

\projectHeading{Engineering Education Scheme}{https://github.com/EdmundGoodman/EES}{Python, Electronics, Manufacturing}{Sept. 2018 -- Apr. 2019}
\begin{bullets}  % \begin{itemize}[leftmargin=*, noitemsep]
    \item Lead the software aspect of the school ``Engineering Education Scheme'' entry, building an autonomous tennis ball collecting \href{https://drive.google.com/file/d/1t9qVtQVATlVSCroJkCgrlD1hFjH6NqUE/view}{\underline{robot}} to the help sports teachers.
    \item Implemented first principles \textbf{image recognition} for tennis balls, and wrote a search algorithm to collect them, along with contributing to the hardware aspect, by manufacturing parts of the shell, and battery and flywheel mountings.
\end{bullets}  % \end{itemize}
\sectionsep

\projectHeading{Rouse Research}{https://github.com/EdmundGoodman/rouse-research/blob/master/Rouse\%20Essay.pdf}{Python, Numpy, Neural networks}{Sept. 2018 -- Apr. 2019}
\begin{bullets}  % \begin{itemize}[leftmargin=*, noitemsep]
    \item Received a Distinction for an essay titled ``How effective are machine learning algorithms compared to traditional analytical techniques with respect to playing abstract games''.
    \item Derived the mathematical foundations of \textbf{back-propagating neural networks} from first principles, and implemented neural networks, and genetic and tree search algorithms to play simple games in Python.

\end{bullets}  % \end{itemize}
\sectionsep

%--------------------------------------------------------------
%     Achievements
%--------------------------------------------------------------
\section{Achievements}

 \textbf{Music}{: Trinity Guildhall Grade 8 Trumpet, ABRSM Grade 7 Singing, \href{https://procorda.com/}{\underline{Pro Corda}} national chamber music finalist (trumpet dectet), previous head chorister of Jesus College Choir.} \\
 \textbf{Cyber Discovery}{: Finalist to the ``Elite'' phase in 2017-19 of \href{https://joincyberdiscovery.com/}{\underline{Cyber Discovery}}. In 2018 from $\sim$30,000 I was one of $\sim$180 selected for the SANS course \href{https://www.sans.org/cyber-security-courses/hacker-techniques-incident-handling/}{\underline{SEC504}}: ``Hacker Tools, Techniques, Exploits, and Incident Handling'', and its associated GIAC certification. In 2019 from $\sim$70,000 I was one of $\sim$240 selected for \href{https://www.sans.org/cyber-security-courses/windows-forensic-analysis/}{\underline{FOR500}}: ``Windows Forensic Analysis''.} \\
 \textbf{Gold Crest award, and Gold level industrial cadet}{: Awarded following completing the above EES project.} \\
 \textbf{Cadet Sergeant, Air Cadet Leadership Course graduate}{: Held responsibility over other cadets, and was one of $\sim$240 each year to graduate a demanding week long course at RAF Cranwell teaching practical leadership skills.}

\end{document}
