%-------------------------
% Resume in Latex
% Original Designer : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% Content Author: Edmund Goodman
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\title{CV}
\author{Edmund Goodman}
\date{October 2020}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \small #1 & \small #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Edmund Goodman} \\ \vspace{1pt}
    \href{mailto:egoodman3141@gmail.com}{\underline{egoodman3141@gmail.com}} $|$
    \href{https://www.linkedin.com/in/EdmundGoodman}{\underline{linkedin.com/in/EdmundGoodman}} $|$
    \href{https://github.com/EdmundGoodman}{\underline{github.com/EdmundGoodman}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{Warwick University}}{Sept. 2020 -- Present}
      {BSc Computer Science with intercalated year: First year, 1st (80.8\%)}{Coventry, England}
    \resumeSubheading
      {\textbf{The Perse Sixth Form}}{Sept. 2018 - Jun. 2020}
      {Academic scholarship, Senior music colours, A-levels in Maths (D2, eq. A*), Further}{Cambridge, England}
      \newline\newline\textit{Maths (D3, eq. A*/A), Physics (D1, eq. high A*) and Computer Science (A*)}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
    {\textbf{iGEM Competitor} $|$ \emph{HTML, SCSS, Javascript, Hugo, Python}}{Feb. 2021 -- Sept. 2021}
    {University of Warwick}{Coventry, England}
    \resumeItemListStart
       \resumeItem{Designed the assessed \href{https://2021.igem.org/Team:Warwick}{\underline{wiki website}}, and implemented a \href{https://github.com/EdmundGoodman/Warwick_modelling}{\underline{model of antibiotic resistant pathogens spread}}}
    \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineering Intern} $|$ \emph{Python, Java, Excel with VBA}}{Jul. 2020 -- Sept. 2020}
      {HUBER+SUHNER Polatis}{Cambridge, England}
      \resumeItemListStart
        \resumeItem{Refactored the VBA backend of an Excel spreadsheet used for corporate planning, created visual representations for the aforementioned planning data}
        \resumeItem{Updated a testing harness for fibre optic switches from Python 2 to Python 3, and wrote a Java implementation of \href{https://tools.ietf.org/html/rfc8071}{\underline{NETCONF call home}} within the open source ONOS project}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineering Work Experience} $|$ \emph{Python, Git}}{Jul. 2017}
      {Argon Design}{Cambridge, England}
      \resumeItemListStart
        \resumeItem{Refactored and redesigned an information display board, converting a monolithic file into a series of microservices running with a Python LAMP server, in order to serve the updated UI}
    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
      {\textbf{Computer Science Revision Guide} $|$ \emph{Markdown, Java, Haskell, Git}}{Apr. 2021 -- Present}
      \resumeItemListStart
        \resumeItem{Co-founded and administrated an open source revision resource for the first year Warwick computer science course, used by over 100 students, and with contributions from over 25 - \href{https://warwick.guide/}{\underline{Project link}}}
        \resumeItem{Managed pull requests and issues following open source best practices, communicated with the university to ensure the project was acceptable, and contributed to the notes for every module I took}
      \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Engineering Education Scheme} $|$ \emph{Python}}{Sept. 2018 -- Apr. 2019}
          \resumeItemListStart
            \resumeItem{Lead the software aspect of the school ``Engineering Education Scheme'' entry, building an autonomous tennis ball collector to the help sports teachers - \href{https://github.com/EdmundGoodman/EES}{\underline{Project link}}, \href{https://drive.google.com/file/d/1t9qVtQVATlVSCroJkCgrlD1hFjH6NqUE/view}{\underline{Video}}}
            \resumeItem{Implemented first principles image recognition for tennis balls, and wrote a search algorithm to collect them, along with contributing to the hardware aspect, by manufacturing parts of the shell, and battery and flywheel mountings}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Rouse Research} $|$ \emph{Python}}{Sept. 2018 -- Apr. 2019}
          \resumeItemListStart
            \resumeItem{Received a Distinction for a project titled ``How effective are machine learning algorithms compared to traditional analytical techniques with respect to playing abstract games'' - \href{https://github.com/EdmundGoodman/rouse-research}{\underline{Project link}}}
            \resumeItem{Derived back-propagating neural networks from first principles, and implemented neural networks, and genetic and tree search algorithms to play simple games}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%
%-----------ACHEIVEMENTS-----------
\section{Acheivements}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Music}{: Trinity Guildhall Grade 8 Trumpet, ABRSM Grade 7 Singing, \href{https://procorda.com/}{\underline{Pro Corda}} national chamber music finalist (trumpet dectet), previous head chorister of Jesus College Choir} \\
     \textbf{Cyber Discovery}{: Finalist to the ``Elite'' phase in 2017-19 of \href{https://joincyberdiscovery.com/}{\underline{Cyber Discovery}}. In 2018 from $\sim$30,000 I was one of $\sim$180 selected for the SANS course \href{https://www.sans.org/cyber-security-courses/hacker-techniques-incident-handling/}{\underline{SEC504}}: ``Hacker Tools, Techniques, Exploits, and Incident Handling'', and it's associated GIAC certification. In 2019 from $\sim$70,000 I was one of $\sim$240 selected for \href{https://www.sans.org/cyber-security-courses/windows-forensic-analysis/}{\underline{FOR500}}: ``Windows Forensic Analysis''} \\
     \textbf{Gold Crest award, and Gold level industrial cadet}{: Awarded following completing the above EES project} \\
     \textbf{Cadet Sergeant, Air Cadet Leadership Course graduate}{: Held responsibility other cadets, and was one of $\sim$240 each year to graduate a demanding week long course at RAF Cranwell teaching practical leadership skills}
    }}
 \end{itemize}



%
%-----------PROGRAMMING SKILLS-----------
%\section{Technical Skills}
% \begin{itemize}[leftmargin=0.15in, label={}]
%    \small{\item{
%     \textbf{Languages}{: Python, Java, Haskell, Bash/Zsh, C, VBA, Javascript, BASIC, PHP, HTML, CSS, SQL} \\
%    }}
% \end{itemize}


%-------------------------------------------
\end{document}
