%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
% \addtolength{\oddsidemargin}{-0.75in}
% \addtolength{\evensidemargin}{-0.75in}
% \addtolength{\textwidth}{1.5in}
% \addtolength{\topmargin}{-.75in}
% \addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Edmund Goodman} \\ \vspace{1pt}
    \href{mailto:egoodman3141@gmail.com}{\underline{egoodman3141@gmail.com}} $|$
    \href{https://www.linkedin.com/in/EdmundGoodman}{\underline{linkedin.com/in/EdmundGoodman}} $|$
    \href{https://github.com/EdmundGoodman}{\underline{github.com/EdmundGoodman}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
  \vspace{-2pt}\item
      \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{University of Warwick} & Sept. 2020 -- Jun. 2024 \\
        \textit{\small{Computer Science BSc (Hons) with intercalated year at Apple Inc.}} & \textit{\small{Coventry \& St Albans, UK}} \\
        \textit{\small{Grades: 80.8\% (first year), 78.4\% (second year)}} & \\
      \end{tabular*}\vspace{-7pt}
    % \resumeSubheading
    %   {University of Warwick}{Sept. 2020 -- Jun. 2024}
    %   {Computer Science BSc (Hons) with intercalated year in industry; Grades: 80.8\%,78.4\%}{Coventry \& St Albans, UK}

    \vspace{-2pt}\item
      \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{The Perse Sixth Form} & Sept. 2018 -- Jun. 2020 \\
        \textit{\small{Academic scholarship; A-levels in Maths (D2, eq. A*), Further Maths (D3, eq. A*/A),}} & \textit{\small{Cambridge, UK}} \\
        \textit{\small{Physics (D1, eq. high A*), and Computer Science (A*)}} & \\
      \end{tabular*}\vspace{-7pt}
    % \resumeSubheading
    %   {The Perse Sixth Form}{Sept. 2018 -- Jun. 2020}
    %   {Academic scholarship; A-levels in Maths (D2, eq. A*), Further Maths (D3, eq. A*/A), Physics (D1, eq. high A*)}{Cambridge, UK}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Employment}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {Apple Inc. $|$ CAD Design Verification Intern}{Jul. 2022 -- Jun. 2023}
      \resumeItemListStart
        \resumeItem{Intercalated year in industry at the UK Design Centre for Apple Silicon in St Albans.}
        \resumeItem{Built software tools and infrastructure for the design and design verification of computer hardware.}
      \resumeItemListEnd
    \resumeProjectHeading
      {HUBER+SUHNER Polatis $|$ Software Engineering Intern}{Jul. 2020 -- Sept. 2020}
      \resumeItemListStart
        \resumeItem{Performed and resolved errors introduced by a major version bump of \texttt{python} for fibre-optic switch test harnesses.}
        \resumeItem{Refactored the \texttt{VBA} backend of a corporate planning spreadsheet.}
      \resumeItemListEnd
      \resumeSubHeadingListEnd

\section{Experience}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {University of Warwick Computing Society $|$ Academic Coordinator}{Sept. 2023 -- Jun. 2024}
      \resumeItemListStart
        \resumeItem{Responsible for organising and delivering technical and industry talks, introductory workshops, and revision sessions -- including \href{https://uwcs.co.uk/resources/git-good/}{\underline{\texttt{git} Good}}, \href{https://youtu.be/o1bSND4SSLM}{\underline{CS260 algorithms}}, and \href{https://www.youtube.com/watch?v=9l9hcSIAAtM}{\underline{The Mathematics of Lasagne}}.}
      \resumeItemListEnd
    \resumeProjectHeading
      {University of Warwick iGEM team $|$ iGEM Team Member}{Feb. 2021 -- Sept. 2021}
      \resumeItemListStart
        \resumeItem{Led software for the international gold medal winning Warwick team for the iGEM synthetic biology competition.}
        \resumeItem{Designed and implemented a stochastic model of the spread of antibiotic resistant pathogens which was nominated for best model (\href{https://2021.igem.org/Team:Warwick/Model}{\underline{2021.igem.org/Team:Warwick/Model}}), and created the wiki website showcasing the team's work.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {Computer Science Revision Guide}{Apr. 2021 -- Jul. 2021}
      \resumeItemListStart
        \resumeItem{Co-created and administrated an open source revision resource (\href{https://warwick.guide/}{\underline{warwick.guide/}}) for the first year Warwick computer science course, used by over one hundred students, and with contributions from over twenty-five.}
        \resumeItem{Managed pull requests and issues following open source best practices, communicated with the university to ensure the project was acceptable, and contributed to the notes for every module I took.}
      \resumeItemListEnd

    \resumeProjectHeading
      {Engineering Education Scheme}{Sept. 2018 -- Apr. 2019}
      \resumeItemListStart
        \resumeItem{Lead the software aspect of the school ``Engineering Education Scheme'' entry, building an autonomous tennis ball collecting \href{https://drive.google.com/file/d/1t9qVtQVATlVSCroJkCgrlD1hFjH6NqUE/view}{\underline{robot}} to the help sports teachers. (\href{https://github.com/EdmundGoodman/EES}{\underline{github.com/EdmundGoodman/EES}})}
        \resumeItem{Implemented first principles image recognition for tennis balls, and wrote a search algorithm to collect them, along with contributing to the hardware aspect by manufacturing parts of the shell, battery, and flywheel mountings.}
      \resumeItemListEnd

    \resumeProjectHeading
      {Caius College Engineering Essay Prize}{May. 2019 -- Sept. 2019}
      \resumeItemListStart
        \resumeItem{Awarded 1st place in the Caius College engineering essay contest, with an entry titled "Powering the UK's electricity supply - distributed systems to enhance the viability of renewable power". (\href{https://www.cai.cam.ac.uk/news/winners-announced-2019-caius-prizes}{\underline{www.cai.cam.ac.uk/news/winners-...}})}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%
%-----------ACHEIVEMENTS-----------
\section{Achievements}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Music}{: Trinity Guildhall Grade 8 Trumpet, ABRSM Grade 7 Singing, \href{https://procorda.com/}{\underline{Pro Corda}} national chamber music finalist (trumpet dectet), previous head chorister of Jesus College Choir.} \\
     \textbf{Cyber security}{: Finalist to the ``Elite'' phase in 2017-19 of \href{https://joincyberdiscovery.com/}{\underline{Cyber Discovery}}. In 2018 from $\sim$30,000 I was one of $\sim$180 selected for the SANS course \href{https://www.sans.org/cyber-security-courses/hacker-techniques-incident-handling/}{\underline{SEC504}}: ``Hacker Tools, Techniques, Exploits, and Incident Handling'', and it's associated GIAC certification. In 2019 from $\sim$70,000 I was one of $\sim$240 selected for \href{https://www.sans.org/cyber-security-courses/windows-forensic-analysis/}{\underline{FOR500}}: ``Windows Forensic Analysis''.} \\
     \textbf{Gold Crest award, and Gold level industrial cadet}{: Awarded following completing the above EES project.} \\
     \textbf{Cadet Sergeant, Air Cadet Leadership Course graduate}{: Held responsibility over other cadets, and was one of $\sim$240 each year to graduate a demanding week long course at RAF Cranwell teaching practical leadership skills.}
    }}
 \end{itemize}



%
%-----------PROGRAMMING SKILLS-----------
%\section{Technical Skills}
% \begin{itemize}[leftmargin=0.15in, label={}]
%    \small{\item{
%     \textbf{Languages}{: Python, Java, Haskell, Bash/Zsh, C, VBA, Javascript, BASIC, PHP, HTML, CSS, SQL} \\
%    }}
% \end{itemize}



%-------------------------------------------
\end{document}
